Tutkielman otsikko

### 2020-01-29 gradu/msc_english_contents.tex
adds large number packaging
Changes exponent
added outline
adds gradu

\chapter{Introduction}

The following gives some superficial instructions for using this template for a Master's thesis. For guidelines on thesis writing you can consult various sources, for example, the Bachelor thesis template.

The thesis should have an introduction chapter. Other chapters can be named according to the topic. In the end, some summary chapter is needed; see Chapter~\ref{chapter:conclusions} for an example.

\chapter{Figures and Tables}

\section{Figures}
Figure~\ref{fig:logo} gives an example how to add figures to the document. Remember always to cite the figure in the main text.

@@

\begin{table}
\centering
\caption{Experimental results.\label{table:results}}
\begin{tabular}{l||l c c r} 
Experiment & 128 & 256 & 32768 & 65536 \\ 
\hline \hline 
$7bit VByte encoding$ & 34.97 & 49 & 53.04 & 52.18\\
$8bit VByte encoding$ & 33.57 & 32.47 & 42.96 & 43.11\\
$7bit VByte encoding with array$ & 33.39 & 46.85 & 51.24 & 49.03\\
$8bit VByte encoding with array$ & 32.52 & 31.88 & 41.54 & 39.94\\

@@

References are listed in a separate .bib-file. In this case it is named \texttt{bibliography.bib} including the following content:
\begin{verbatim}
@article{einstein,
    author =       "Albert Einstein",
    title =        "{Zur Elektrodynamik bewegter K{\"o}rper}. ({German})
        [{On} the electrodynamics of moving bodies]",
    journal =      "Annalen der Physik",
    volume =       "322",
    number =       "10",
    pages =        "891--921",
    year =         "1905",
    DOI =          "http://dx.doi.org/10.1002/andp.19053221004"
}

>>>>

\chapter{Introduction}
Enormous datasets are a common case in today's applications. Compressing the datasets is beneficial, because they 
naturally decrease memory requirements but also are faster when compressed data is read from disk \citep{Zob95}.

One of the leading methods of data compression is variable-length coding \citep{Sal99}, where frequent sequences of data
are represented with shorter codewords. Because the sequences of data have different lenghts when compressed, it is 
not trivial to determine the exact location of a certain element. If this is required, the usual data compression algorithms are
inefficient. Fortunately this is not a requirement compression algorithms usually need to fulfill.

However, random access of compressed data is needed in compressed data structures. In most compression methods, the only way 
to this is to decompress data from the beginning. An integer compressing method with fast random access is explained and compared
existing state-of-the-art methods.

\chapter{Basic Concepts}
Variable-byte encoding \citep{Wil99} is a method of compressing integers. It splits an integer into blocks of $b$ bits and then encodes
the block as $b + c$. $c$ is a bit denoting whether $b$ has the most significant bits of the number or not. A good dataset for variable-byte encoding
is a set with both very small and very large numbers, since he compression comes from omitting the leading zeros in the bit array. This method 
loses in compression performance to other methods \citep{Bri09}, but they are very fast to decode and allow fast random access.

- Explain rank / select

\chapter{Previous Work}
bl
\chapter{Algorithm}
here
\chapter{Results}
hmll
\section{Figures}
Figure~\ref{fig:logo} gives an example how to add figures to the document. Remember always to cite the figure in the main text.

@@

\begin{table}
\centering
\caption{Results with 100k entries (in milliseconds).\label{table:results}}
\begin{tabular}{l||l c c c c r} 
Experiment & 128 & 256 & 32768 & 65536 & $2^{24}$ & $2^{32} -1$\\ 
\hline \hline 
$7bit VByte encoding$ & 34.97 & 49 & 53.04 & 52.18 & 53.08 & 76.21\\
$8bit VByte encoding$ & 33.57 & 32.47 & 42.96 & 43.11 & 46.15 & 65.14\\
$7bit VByte encoding with array$ & 33.39 & 46.85 & 51.24 & 49.03 & 48.93 & 66.84 \\
$8bit VByte encoding with array$ & 32.52 & 31.88 & 41.54 & 39.94 & 41.15 & 52.86 \\

\begin{table}
\centering
\caption{Results with 1M entries (in milliseconds).\label{table:results}}
\begin{tabular}{l||l c c c c r} 
Experiment & 128 & 256 & 32768 & 65536 & $2^{24}$ & $2^{32} -1$ \\ 
\hline \hline 
$7bit VByte encoding$ & 38.17 & 55.09 & 64.38 & 65.36 & 68.08 & 159 \\
$8bit VByte encoding$ & 37.09 & 37.75 & 53.44 & 54.6 & 59.32 & 148.7\\
$7bit VByte encoding with array$ & 38.09 & 55.42 & 62.22 & 61.25 & 71.72 & 135.01\\
$8bit VByte encoding with array$ & 36.13 & 36.83 & 50.58 & 50.73 & 56.93 & 103.18\\

@@

References are listed in a separate .bib-file. In this case it is named \texttt{bibliography.bib} including the following content:
\begin{verbatim}

@article{einstein,
    author =       "Albert Einstein",
    title =        "{Zur Elektrodynamik bewegter K{\"o}rper}. ({German})
        [{On} the electrodynamics of moving bodies]",
    journal =      "Annalen der Physik",
    volume =       "322",
    number =       "10",
    pages =        "891--921",
    year =         "1905",
    DOI =          "http://dx.doi.org/10.1002/andp.19053221004"
}
